Abstractions for Multi-Sorted Substitutions

### 2023-08-30 paper/paper.tex
Update.

  But to unify those two compositions, we need a new abstraction.

  \ExampleCode\KComposition

>>>>

  But to unify those two compositions, we need a new abstraction:
  \ExampleCode\KComposition
  The Kit-abstraction from before allowed us to abstract over what we
  apply, i.e.\ a renaming or a substitution, but not about what we apply it
  to, i.e.\ a variable or a term. For the latter we still have two
  distinct operations \ACode{\ADef{\_\&\_}} and \ACode{\ADef{\_⋯\_}}.
  A \ACode{\ACon{ComposeKit} K₁ K₂ K₁⊔K₂} fills exactly that gap by providing
  the operation \ACode{\ADef{\_\&/⋯\_}} which applies a renaming/substitution (\ACode{K₂})
  to a variable/term (\ACode{K₁}) and produces a variable/term (\ACode{K₁⊔K₂}).
